
The optimal approach for this task would be to follow a systematic and structured process to develop a multiple regression model to predict the compressive strength of concrete. This process can be broken down into the following steps:

Data cleaning and preparation: This involves checking for missing values, outliers, and data consistency issues. It may also involve transforming the data to ensure it meets the assumptions of the regression model.

Exploratory data analysis: This involves visualizing the data and identifying patterns and relationships between the independent variables and the dependent variable.

Feature selection: This involves selecting the most relevant independent variables that have a significant impact on the dependent variable.

Model building: This involves building a multiple regression model using the selected independent variables and the dependent variable.

Model evaluation: This involves evaluating the performance of the regression model using various statistical measures such as R-squared, adjusted R-squared, mean squared error, and root mean squared error.

Model refinement: This involves refining the model by adding or removing independent variables, transforming the data, or using different modeling techniques.
```{r}
# install packages
# install.packages("readxl")
# install.packages("patchwork")
# install.packages("cowplot")

```

```{r}

library(readxl)
library(patchwork)
library(cowplot)
```

```{r}
# load data
data <- read_excel("data.xlsx")
```

```{r}
# check data
head(data)
```

```{r}
# x=check for missing values
sum(is.na(data))

```


```{r}
# chceck duolicate data
sum(duplicated(data))

```


```{r}
# unique duolicate records
data <- unique(data)

```



```{r}
str(data)

```


```{r}
summary(data)

```




```{r}
library(ggplot2)
library(patchwork)

plots <- list()

for(col in colnames(data)) {
  plot_title <- paste("Distribution of", col)
  x_axis_title <- col
  if (col == "Concrete compressive strength(MPa, megapascals)") {
    x_axis_title <- "Concrete compressive strength (MPa)"
  }
  plot <- ggplot(data, aes(x = .data[[col]])) +
    geom_histogram(binwidth = 5, fill = "blue", color = "black") +
    labs(title = plot_title,
         x = x_axis_title,
         y = "Count") +
    theme(plot.title = element_text(size = 10),
          axis.title.x = element_text(size = 10),
          axis.title.y = element_text(size = 10),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_blank(),
          axis.line = element_line(colour = "black"))
  plots[[col]] <- plot
}

combined_plot <- wrap_plots(plots, ncol = 3)
combined_plot + theme(plot.background = element_rect(fill = "white"), 
                      plot.title = element_text(size = 6, face = "bold"))




```

Lets explore the correlation between the variables

```{r}
library(ggplot2)


# Create a correlation matrix
corr <- round(cor(data), 2)

# Convert the correlation matrix to a dataframe
corr_df <- as.data.frame(as.table(corr))
tail(corr_df, 9)


```




```{r}
# Rename the columns
names(corr_df) <- c("variable1", "variable2", "correlation")

# Create a heatmap with numbers
ggplot(corr_df, aes(variable1, variable2, fill = correlation)) +
  geom_tile() +
  geom_text(aes(label = round(correlation, 2)), color = "black") +
  scale_fill_gradient2(low = "blue", mid = "white", high = "red", midpoint = 0) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```


Cement, Age, and Superplasticizer has the highest positive correlation with concrete comprehensive strength.
Water and Fine Aggregate has the highest negative correlation with the concrete comprehensive strength.

```{r}

# Create a scatter plot between x and y
plot(data$'Concrete compressive strength', data$'Cement', xlab = "Concrete compressive strength", ylab = "Cement", main = "Concrete compressive strength vs Cement")

```
```{r}
# Create a scatter plot between x and y
plot(data$'Concrete compressive strength', data$'Superplasticizer', xlab = "Concrete compressive strength", ylab = "Cement", main = "Concrete compressive strength vs Superplasticizer")

```

```{r}
# Create a scatter plot between x and y
plot(data$'Concrete compressive strength', data$'Age', xlab = "Concrete compressive strength", ylab = "Cement", main = "Concrete compressive strength vs Age")
```


```{r}
# Create a scatter plot between x and y
plot(data$'Concrete compressive strength', data$'Water', xlab = "Concrete compressive strength", ylab = "Cement", main = "Concrete compressive strength vs Water")
```

```{r}
# Create a scatter plot between x and y
plot(data$'Concrete compressive strength', data$'Fine aggregate', xlab = "Concrete compressive strength", ylab = "Cement", main = "Concrete compressive strength vs Fine aggregate")

```





```{r}
ggplot(data, aes( y = `Concrete compressive strength`)) +
  geom_boxplot() +
  labs(y = "Concrete compressive strength(MPa, megapascals)")


```



```{r}
ggplot(data, aes(x = 'Cement', y = `Concrete compressive strength`)) +
  geom_violin() +
  labs(x = "Cement (component 1)(kg in a m^3 mixture)", y = "Concrete compressive strength(MPa, megapascals)")

```


```{r}


# Fit a linear regression model
model <- lm(`Concrete compressive strength` ~ Cement + Slag + Ash + Water + Superplasticizer + `Coarse Aggregate` + `Fine Aggregate` + Age, data = data)

# Print the summary of the model
summary(model)

```

p - vakue for Coarse Aggregate, Fine Aggregate > 0.5
This means that at 95% confidence we can reject the null hypotheses and Coarse Aggregate, Fine Aggregate are insignificant.

